### 2010-03-10 papers/icfp-2010-desc/paper_type_theory.tex
Desc@ICFP: finish up summary of Type Theory section.

\subsection{Type propagation}

@@

@@

@@

\begin{structure}
<- Summary
    -> Not a novel technique [refs?]
        /> Used as a boilerplate scrapper
    -> Make dealing with codes *practical*
        <- Example: Finite sets/finite function space
        -> We should not restrain ourself in using codes
            <- We know how to present them to the user
-> Will extend this machinery in further sections
\end{structure}

>>>>

\subsection{Type propagation}
\label{sec:type-propagation}

@@

%%! This might deserve a more thorough explanation, with snippet of code.

@@

The abstraction we have developed in this section are entirely
transparent to the user. In the case of finite function space, the
user has never to explicitly \emph{call} the $\F{switch}$
eliminator. Nor will she \emph{be presented} the elaborated term, only
the high-level . Bidirectional type-checking and type-directed
pretty-printing seal the low-level type theory behind the high-level
expressions.

@@

\begin{wstructure}
<- Summary
    -> Not a novel technique [refs?]
        /> Used as a boilerplate scrapper
    -> Make dealing with codes *practical*
        <- Example: Finite sets/finite function space
        -> We should not restrain ourself in using codes
            <- We know how to present them to the user
-> Will extend this machinery in further sections
\end{wstructure}

In this section, we have developped a type propagation system, based
on bidirectional type-checking. Using bidirectional type-checking as a
boilerplate scrapper is a well-known technique~\cite{}. In our case,
we have shown how to instrument bidirectionality to rationalize the
expressivity of dependent types. We have illustrated our approach with
finite sets. We have successfully abstracted away the low-level
presentation of finite sets, offering a convenient syntax instead.

This example teaches us that we should not be afraid by codes, as far
as type information is available. We have shown how to rationalize
this information in a formal presentation. Hence, we have proved that
programming with such objects is practical. As we introduce more codes
in our theory, we will show how to extend the framework we have
developped so far.
